Infinite Diameter Confidence Sets in Hedges' Publication Bias Model

### 2020-08-12 infiniteci.tex
:pear: Update.

The most popular and well-known meta-analysis method is the random
effects model with normal likelihoods \citep{hedges1998fixed}. Written
in hierarchical notation, it equals
\begin{eqnarray*}
\theta_{i} & \sim & N(\theta_{0},\tau),\\
x_{i}\mid\theta_{i},\sigma & \sim & N(\theta_{i},\sigma_{i}).
\end{eqnarray*}
Here $\sigma_{i}$ is the standard deviation of the $i$th study.
Following the convention in meta-analysis, we assume all $\sigma_{i}$s
to be known. The mean parameter $\theta$ is the population effect
size, $N(\theta_{0},\tau)$ is the effect size distribution, and $\tau$
is the heterogeneity parameter. The purpose of the effect size distribution
is to model the fact that most effect size estimates plugged into
a meta-analysis do not appear to measure the same phenomenon. By integrating
out $\theta_{i}$, we find the density of $x_{i}$,
\[
f(x_{i};\theta_{0},\tau,\sigma_{i})=\phi(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}}),
\]
where $\phi$ is the density of a normal random variable.

@@

\citet{hedges1992modeling} studies the selection model when $w$
is a step function with fixed steps. Let $\alpha$ be a vector with
elements $0=\alpha_{0}<\alpha_{1}<\ldots<\alpha_{K}=1$ and $\rho$
be a $K$-ary non-negative, non-increasing vector having its first
element equal to $\rho_{1}=1$. Define the step function $w$ based
on $\alpha$ and $\rho$ as
\begin{equation}
w(u;\rho,\alpha)=\sum_{k=1}^{K}\rho_{k}1_{(\alpha_{k-1},\alpha_{k}]}(u).\label{eq:step function}
\end{equation}
We call the selection model with a step function \emph{Hedges' publication
bias model. }Its density is
\begin{equation}
f(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})\propto\sum_{k=1}^{K}\rho_{k}\phi(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})1_{(\alpha_{k-1},\alpha_{k}]}(u_{i}).\label{eq:hedges model}
\end{equation}
Interpretating Hedges' publication bias model is easy. When the editor
receives a study with \emph{p}-value $u$, she finds the $j$ such
that $u\in(\alpha_{j-1},\alpha_{j}]$ and accepts with probability
$\rho_{j}$. Since $\rho_{1}=1$, she always accepts when $u\in[0,\alpha_{1}]$.
The vector $\rho$ is non-increasing since a publication decision
based solely on \emph{p}-values should always act favorably towards
lower \emph{p}-values. The parameters $(\theta_{0},\tau,\rho)$ of
the model are identified when $\alpha$ is fixed \citep[Web Appendix A]{moss2019modelling}.

Hedges' publication bias models allows both for non-significant studies
to be published and allows the editor to act differently towards different
cutoffs such as $\alpha=0.025$ and $\alpha=0.05$. In addition, the
model can approximate any non-increasing selection function $w$ by
increasing the number of steps.

@@

The main benefit of Hedges' publication bias model (\ref{eq:hedges model})
is how it models \emph{p}-values based publication bias directly,
there is no approximation involved. If you believe in the random effects
meta-analysis model and the \emph{p}-value based publication bias
scenario, Hedges' publication bias model is simply the correct model.
Most statistical methods correcting for publication bias in the literature
either do not make use of an explicit statistical model or do not
estimate the parameters $\theta_{0}$ and $\tau$. For instance, the
funnel funnel plot of \citet{Egger1997-rd} is a graphical method,
while the trim-and-fill method of \citet{Duval2000-ct} is a non-parametric
method based on making the funnel plot symmetric. \citet{Stanley2005-ng,stanley2014meta}
discuss various misspecified regression-based estimators of the corrected
effect size $\theta$ based on the fixed effect Hedges' publication
bias model. The estimating \emph{p}-curve method of \citet{Simonsohn2014-cn}
and \emph{p}-uniform of \citet{Van_Assen2015-qs,Van_Aert2016-cu}
are two methods for dealing with publication bias hailing from psychology.
Both are based on a variant of the basic publication bias model, but
with fixed instead of random effects, and both employ somewhat unusual
estimation methods \citep{McShane2016-rb}. Since there is ample evidence
of heterogeneity in meta-analysis, restricting oneself to the fixed
effects meta-analysis is a mistake.

@@

Fix some measurable space $(\Omega,\mathcal{F})$, let $\mathcal{P}$
be a family of dominated probability measures defined on this measurable
space, and $\mathcal{\Pi}$ a partition of $\mathcal{P}$. Recall
that a partition of $\mathcal{P}$ is a collection of disjoint non-empty
subsets $\pi$ of $\mathcal{P}$ such that $\bigcup_{\pi\in\Pi}\pi=\mathcal{P}$.
When $p$ is a density associated with a $P\in\mathcal{P}$, we will
use the standard notation $[p]$ to denote the unique $\pi$ containing
$P$. 
\begin{defn}
\label{def:confidence set} A \emph{confidence set} of level $\alpha$
is a family of rejection sets $\{R(\pi)\},\pi\in\Pi$ such that
\[
\sup_{\pi\in\Pi}\sup_{P\in\pi}P(R(\pi))\leq\alpha.
\]
If the inequality is an equality, the confidence set has \emph{size}
$\alpha$. 
\end{defn}

@@

This is a modified Gleser--Hwang theorem \citep[Theorem 1]{gleser1987nonexistence}
formulated in terms of partitions. Its proof is in the appendix (p.
\pageref{proof:Gleser--Hwang}).
\begin{thm}[Gleser--Hwang theorem]
\label{thm:Gleser--Hwang} Suppose there is a sequence $\{p_{i}\}$
of densities from $\mathcal{P}$ satisfying the following: 
\begin{enumerate}
\item There is a density $p^{\star}$ such that $p_{i}$ converges to $p^{\star}$
pointwise,
\item $\supp p\supseteq\supp p^{\star}$ for all $p$,
\item the size of $[p_{i}]$ goes to infinity, $\left\Vert [p_{i}]\right\Vert \to\infty$.
\end{enumerate}
Then every confidence set with level $\alpha>0$ has infinite diameter
with positive probability.
\end{thm}

Following the terminology of \citet{berger1999integrated}, we will
say that families $\mathcal{P}$ of probabilities satisfying the conclusion
of Theorem \ref{thm:Gleser--Hwang} for some suitable partition $\Pi$
belong to the Gleser--Hwang class. To make the Gleser--Hwang class
more familiar, we will present two examples. More examples can be
found in the papers of \citet{gleser1987nonexistence} and \citet{berger1999integrated}.
\begin{example}[Fieller's problem]
\label{exa:Fieller's problem} Let $X,Y$ be an observation from
a bivariate normal $N([\mu_{1},\mu_{2}],I\sigma^{2})$, where $\sigma^{2}$
is known. We want to form a confidence set for ratio $\mu_{2}/\mu_{1}$.
The most famous confidence set is due to \citet{Fieller1940-lg}.
His confidence set can be finite, the whole real line, or the union
of two disjoint semi-infinite intervals \citep{Koschat1987-dk}, all
with positive probability.

But it is not only Fieller's confidence set that might be infinitely
long. The Gleser--Hwang theorem can be used to show that every confidence
set for $\mu_{2}/\mu_{1}$ must be infinitily long with positive probability.
This result is almost independent of the distribution of $X$ and
$Y$. To state this result in our notation, let $\mathcal{P}$ be
a family of bivariate distributions over $(X,Y)$. All of these distributions
have the same support, and all of them have finite means $E_{p}(X)$
and $E_{p}(Y)$. Moreover, assume $E_{p}(X)=0$ is attainable for
some $p\in\mathcal{P}$. Define the partition $\Pi$ by $p,q\in\pi$
if and only if $E_{p}(X)/E_{p}(Y)=E_{q}(X)/E_{q}(Y)$, and let $\left\Vert [p]\right\Vert =|E_{q}(X)/E_{q}(Y)|$,
i.e., the ratio of means. Choose a sequence $p_{n}(x,y)=p(x,y)$,
where $p(x,y)$ is density with means $E_{p}X>0$ and $E_{p}Y=0$.
Then $\left\Vert [p]\right\Vert =\infty$, the conditions of Theorem
\ref{thm:Gleser--Hwang} are satisfied, and every confidence set with
level $\alpha>0$ has infinite diameter with positive probability.
\begin{example}[Bahadur--Savage]
\label{exa:Bahadur--Savage} \citet{bahadur1956nonexistence} studies
non-parametric testing of the mean, and concludes the mean cannot
be meaningfully tested. They are working with a family $\mathcal{P}$
of densities over $\mathbb{R}$ that covers all finite means, has
finite variances, and is closed under convex combinations. Similar
problems were considered by \citet{romano2004non} and \citet{Donoho1988-hg}.

Using the Gleswer--Hwang theorem, it is easy to verify every confidence
set has infinite diameter with positive probability. Define the partition
$\Pi$ by $p,q\in\Pi$ if and only if $E_{p}(X)=E_{q}(X)$, and let
$\left\Vert [p]\right\Vert =|E_{p}(X)|$. Let
\[
p_{n}(x)=\left(1-\frac{1}{n}\right)q_{0}(x)+\frac{1}{n}q_{n^{2}}(x),
\]
where $p_{0}$ has mean $0$ and $q_{n^{2}}$ has mean $n^{2}$. Then
$\left\Vert [p_{n}]\right\Vert =n$, the conditions of Theorem \ref{thm:Gleser--Hwang}
are satisfied, and every confidence set with level $\alpha>0$ has
infinite diameter with positive probability.
\end{example}

\end{example}

@@

Using Lemma \pageref{lem:generalized shifted exponential} it is not
hard to show that the basic publication bias model (\ref{eq:selection for significance model})
is a member of the Gleser--Hwang class.
\begin{thm}
\label{thm:simple publication bias} Assume $n$ independent samples
from the basic publication bias model (\ref{eq:selection for significance model}).
Then, for any $n$, any confidence set for $\theta_{0},\tau$, or
$(\theta_{0},\tau)$ with level $\alpha>0$ will have infinite diameter
with positive probability. 
\end{thm}

@@

Let $f^{1},f^{2},\ldots,f^{K}$ be a sequence of densities, $\pi=(\pi_{1},\pi_{2},\ldots,\pi_{K})$
a probability vector, and $p=\sum_{k\leq K}\pi^{k}f^{k}$ a mixture
distribution. We will assume that the size of $[p]$ equals the size
of any of its mixture components $[f^{k}]$ for some size $\left\Vert \cdot\right\Vert $,
i.e., $\left\Vert [p]\right\Vert =\left\Vert [f^{k}]\right\Vert $
for all $k$. Why we do this will be clear in the proof of Theorem
\ref{thm:general publication bias}, but think of it this way: If
all of $p$s mixture components have the same mean, the mean of $p$
equals the mean of any $f^{k}$. 
\begin{lem}
\label{prop:Mixture model corollary} Let $\mathcal{P}$ be a class
of $K$-ary mixture distributions and $||[p]||$ be the assumption
above. Assume there is a sequence $p_{i}=\sum_{k\leq K}\pi_{i}^{k}f_{i}^{k}$
and a subset $K'$ such that 
\begin{enumerate}
\item For all $k\in K'$, there is a density $f^{k\star}$ such that $f_{i}^{k}$
converges to $f^{k\star}$ pointwise.
\item For all mixtures $p$, $\supp p\supseteq\supp f^{k\star}$ for some
$k\in K'$.
\item For all $k\in K'$, the size of $[f_{i}^{k}]$ goes to infinity, $\left\Vert [f_{i}^{k}]\right\Vert \to\infty$.
\item The density concentrates on the components indexed by $K'$, $\lim_{i\to\infty}\sum_{k\in K'}\pi_{i}^{k}=1$.
\end{enumerate}
Then every confidence set with level $\alpha>0$ has infinite diameter
with positive probability.
\end{lem}

\begin{proof}
We employ Theorem \ref{thm:Gleser--Hwang}. By (i) and (iv), $p_{i}$
converges pointwise to the density $\sum_{k\in K'}\pi_{i}^{k\star}f_{i}^{k\star}=p^{\star}$
. That $\supp p\supseteq p^{\star}$ follows from (ii) and (iv). Finally,
from the assumption that$\left\Vert [p]\right\Vert =\left\Vert [f_{k}]\right\Vert $,
we get that $\left\Vert [p]\right\Vert \to\infty$ too. 
\end{proof}
\begin{thm}
\label{thm:general publication bias} Assume $n$ independent samples
from the publication bias model (\ref{eq:selection for significance model}),
where the selection probability $\rho$ is unknown and $\alpha$ is
known. Then any confidence set for $\theta_{0},\tau$, or $(\theta_{0},\tau)$
will have infinite diameter with positive probability.
\end{thm}

\begin{proof}
\label{proof:general publication bias} Let $n=1$ and consider confidence
sets for $\theta_{0}$. Let $\Pi$ be the partition of $\mathcal{P}$
where $p,q\in\pi$ if and only if they share the same $\theta_{0}$,
and let $||[p]||=|\theta_{0}|$. Then $||f^{k}||=|\theta_{0}|$ from
the mixture representation (\ref{eq:mixture model formulation}).
Using Lemma \ref{lem:generalized shifted exponential}, we see that
$f^{k},k>1$ converges pointwise to a truncated exponential when $\theta_{0}=-n$
and $\sqrt{\tau^{2}+\sigma^{2}}=n^{1/2}$, so that (i), (ii), (iii)
of Proposition \ref{prop:Mixture model corollary} are satisfied with
$K'=K\backslash\{1\}$. The mixture probabilities for $k\neq K$ can
be fixed at e.g. $\pi=1/(K-1)$, and (iv) is satisfied as well. The
proofs for $||[p]||=\tau$ and $||[p]||=\sqrt{\tau^{2}+\theta_{0}^{2}}$
are similar and omitted. When $n>1$, expand the expression $\prod_{j=1}^{n}\sum_{k\leq K}\pi_{i}^{k}(\sigma_{j})f_{i}^{k}(\sigma_{j}),$and
use the same reasoning as in the first part of this proof.
\end{proof}

@@

The following sandwich convergence theorem is used in the proof of
the Gleser--Hwang theorem. 
\begin{lem}[{\citet[Exercise 16.4(a)]{billingsley1995probability}}]
\label{lem:Dominated covergence theorem} Suppose $a_{n},b_{n},f_{n}$
converge to $a,b,f$ and $a_{n}\leq f_{n}\leq b_{n}$ for all $n$.
If $\int a_{n}d\mu\to\int ad\mu$ and $\int b_{n}d\mu\to\int bd\mu$,
then $\int f_{n}d\mu\to\int fd\mu$.
\end{lem}

The proof of Theorem \ref{thm:Gleser--Hwang} follows the proof of
\citet[Theorem 1]{gleser1987nonexistence} closely. 
\begin{proof}[Proof of Theorem \ref{thm:Gleser--Hwang}]
\label{proof:Gleser--Hwang}We can assume without loss of generality
that $\left\Vert [p_{n}]\right\Vert \geq n$, as we can choose a subsequence
if we have to. By definition of the diameter $D$ (\ref{eq:diameter})
we see that
\[
\{D\geq n\}=\{\omega\in\Omega\mid\textrm{there is a }\pi\textrm{ such that}\left\Vert \pi\right\Vert \geq n\textrm{ and }\omega\in R^{c}(\pi)\},
\]
and if $||[p_{n}]||\geq n$, then $R^{c}([p_{n}])\subseteq\{D\geq n\}$.
Since we assume that $\left\Vert [p_{n}]\right\Vert \geq n$ and 
\[
1-\alpha\leq P_{n}(R^{c}([p_{n}]))=\int_{R^{c}([p_{n}])}p_{n}d\mu
\]
by definition of a confidence set, we have that
\begin{equation}
0<1-\alpha\leq\int_{R^{c}([p_{n}])}p_{n}d\mu\leq\int_{D\geq n}p_{n}d\mu\label{eq:inequality with R^c}
\end{equation}
for all $n$. Since $p_{n}$ and $p^{\star}$ are densities,
\[
\lim_{n\to\infty}\int p_{n}d\mu=1=\int p^{\star}d\mu=\int\lim_{n\to\infty}p_{n}d\mu.
\]
This allows us to use Lemma \ref{lem:Dominated covergence theorem}
with $a_{n}=0$, $b_{n}=p_{n}$, and $f_{n}=1_{D\geq n}p_{n}$ and
conclude that

>>>>

The most popular and well-known meta-analysis method is the random
effects model with normal likelihoods \citep{hedges1998fixed}. Written
in hierarchical notation, it equals
\begin{eqnarray*}
\theta_{i} & \sim & N(\theta_{0},\tau),\\
x_{i}\mid\theta_{i},\sigma & \sim & N(\theta_{i},\sigma_{i}).
\end{eqnarray*}
Here $x_{i}$ is the effect size and $\sigma_{i}$ is the standard
deviation of the $i$th study, and $i=1,\ldots,N$. Following the
convention in meta-analysis, we assume all $\sigma_{i}$s to be known.
The mean parameter $\theta$ is the population effect size, $N(\theta_{0},\tau)$
is the effect size distribution, and $\tau$ is the heterogeneity
parameter. The purpose of the effect size distribution is to model
the fact that most effect size estimates plugged into a meta-analysis
do not appear to measure the same phenomenon. By integrating out $\theta_{i}$,
we find the density of $x_{i}$,
\[
f(x_{i};\theta_{0},\tau,\sigma_{i})=\phi(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}}),
\]
where $\phi$ is the density of a normal random variable.

@@

\citet{hedges1992modeling} studies the selection model when $w$
is a step function with fixed steps. Let $\alpha$ be a vector with
elements $0=\alpha_{0}<\alpha_{1}<\ldots<\alpha_{K}=1$ and $\rho$
be a $K$-ary non-negative, non-increasing vector having its first
element equal to $\rho_{1}=1$. Define the step function $w$ based
on $\alpha$ and $\rho$ as
\begin{equation}
w(u;\rho,\alpha)=\sum_{k=1}^{K}\rho^{k}1_{(\alpha_{k-1},\alpha_{k}]}(u).\label{eq:step function}
\end{equation}
We call the selection model with a step function \emph{Hedges' publication
bias model. }Its density is
\begin{equation}
f(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})\propto\sum_{k=1}^{K}\rho^{k}\phi(x_{i};\theta_{0},\sqrt{\tau^{2}+\sigma_{i}^{2}})1_{(\alpha_{k-1},\alpha_{k}]}(u_{i}).\label{eq:hedges model}
\end{equation}
Interpretating Hedges' publication bias model is easy. When the editor
receives a study with \emph{p}-value $u$, she finds the $k$ such
that $u\in(\alpha_{k-1},\alpha_{k}]$ and accepts with probability
$\rho^{k}$. Since $\rho^{1}=1$, she always accepts when $u\in[0,\alpha_{1}]$.
The vector $\rho$ is non-increasing since a publication decision
based solely on \emph{p}-values should always act favorably towards
lower \emph{p}-values. The parameters $(\theta_{0},\tau,\rho)$ of
the model are identified when $\alpha$ is fixed \citep[Web Appendix A]{moss2019modelling}.

Hedges' publication bias model allows both for non-significant studies
to be published and allows the editor to act differently towards different
cutoffs such as $\alpha=0.025$ and $\alpha=0.05$. In addition, the
model can approximate any non-increasing selection function $w$ by
increasing the number of steps.

@@

The main benefit of Hedges' publication bias model (\ref{eq:hedges model})
is how it models \emph{p}-values based publication bias directly,
there is no approximation involved. If you believe in the random effects
meta-analysis model and the \emph{p}-value based publication bias
scenario, Hedges' publication bias model is simply the correct model.
Most statistical methods correcting for publication bias in the literature
either do not make use of an explicit statistical model or do not
estimate the parameters $\theta_{0}$ and $\tau$. For instance, the
funnel plot of \citet{Egger1997-rd} is a graphical method, while
the trim-and-fill method of \citet{Duval2000-ct} is a non-parametric
method based on making the funnel plot symmetric. \citet{Stanley2005-ng,stanley2014meta}
discuss various misspecified regression-based estimators of the corrected
effect size $\theta$ based on the fixed effect Hedges' publication
bias model. The estimating \emph{p}-curve method of \citet{Simonsohn2014-cn}
and \emph{p}-uniform of \citet{Van_Assen2015-qs,Van_Aert2016-cu}
are two methods for dealing with publication bias hailing from psychology.
Both are based on a variant of the basic publication bias model, but
with fixed instead of random effects, and both employ somewhat unusual
estimation methods \citep{McShane2016-rb}. Since there is ample evidence
of heterogeneity in meta-analysis, restricting oneself to the fixed
effects meta-analysis is a mistake.

@@

Fix some measurable space $(\Omega,\mathcal{F})$, let $\mathcal{P}$
be a family of dominated probability measures defined on this measurable
space, and $\Pi$ a partition of $\mathcal{P}$. Recall that a partition
of $\mathcal{P}$ is a collection of disjoint non-empty subsets $\pi$
of $\mathcal{P}$ such that $\bigcup_{\pi\in\Pi}\pi=\mathcal{P}$.
When $p$ is a density associated with a $P\in\mathcal{P}$, we will
use the standard notation $[p]$ to denote the unique $\pi$ containing
$P$. 
\begin{defn}
\label{def:confidence set} A \emph{confidence set} of level $\alpha$
is a family of rejection sets $\{R(\pi)\},\pi\in\Pi$ such that
\[
\sup_{\pi\in\Pi}\sup_{P\in\pi}P(R(\pi))\leq\alpha.
\]
If the inequality is an equality, the confidence set has \emph{size}
$\alpha$. 
\end{defn}

@@

This is a modified Gleser--Hwang theorem \citep[Theorem 1]{gleser1987nonexistence}
formulated in terms of partitions. Its proof is in the appendix (p.
\pageref{proof:Gleser--Hwang}).
\begin{thm}[Gleser--Hwang theorem]
\label{thm:Gleser--Hwang} Suppose there is a sequence $\{p_{n}\}$
of densities from $\mathcal{P}$ satisfying the following: 
\begin{enumerate}
\item There is a density $p^{\star}$ such that $p_{n}$ converges to $p^{\star}$
pointwise,
\item $\supp p\supseteq\supp p^{\star}$ for all densities $p$ derived
from $\mathcal{P}$,
\item the size of the equivalence class $[p_{n}]$ goes to infinity as $n$
increases, $\left\Vert [p_{n}]\right\Vert \to\infty$.
\end{enumerate}
Then every confidence set with level $\alpha>0$ has infinite diameter
with positive probability.
\end{thm}

Following the terminology of \citet{berger1999integrated}, we will
say that families $\mathcal{P}$ of probabilities satisfying the conclusion
of Theorem \ref{thm:Gleser--Hwang} for a suitable partition $\Pi$
belong to the Gleser--Hwang class. To make the Gleser--Hwang class
more familiar, we will present two examples. More examples can be
found in the papers of \citet{gleser1987nonexistence} and \citet{berger1999integrated}.

Fieller's problem is the best known case of a badly behaved confidence
set. Let $X,Y$ be an observation from a bivariate normal $N([\mu_{1},\mu_{2}],I\sigma^{2})$,
where $\sigma^{2}$ is known. We want to form a confidence set for
the ratio $\mu_{2}/\mu_{1}$. The most famous confidence set is due
to \citet{Fieller1940-lg}. His confidence set can be finite, the
whole real line, or the union of two disjoint semi-infinite intervals
\citep{Koschat1987-dk}, all with positive probability.

But it is not only Fieller's confidence set that might be infinitely
long. The Gleser--Hwang theorem can be used to show that every confidence
set for $\mu_{2}/\mu_{1}$ must be infinitily long with positive probability.
This result is almost independent of the distribution of $X$ and
$Y$. To state this result in our notation, let $\mathcal{P}$ be
a family of bivariate distributions over $(X,Y)$. All of these distributions
have the same support, and all of them have finite means $E_{p}(X)$
and $E_{p}(Y)$. Moreover, assume $E_{p}(X)=0$ is attainable for
some $p\in\mathcal{P}$. Define the partition $\Pi$ by $p,q\in\pi$
if and only if $E_{p}(X)/E_{p}(Y)=E_{q}(X)/E_{q}(Y)$, and let $\left\Vert [p]\right\Vert =|E_{q}(X)/E_{q}(Y)|$,
i.e., the ratio of means. Choose a sequence $p_{n}(x,y)=p(x,y)$,
where $p(x,y)$ is density with means $E_{p}X>0$ and $E_{p}Y=0$.
Then $\left\Vert [p]\right\Vert =\infty$, the conditions of Theorem
\ref{thm:Gleser--Hwang} are satisfied, and every confidence set with
level $\alpha>0$ has infinite diameter with positive probability.

\citet{bahadur1956nonexistence} studies non-parametric testing of
the mean, and concludes the mean cannot be meaningfully tested. They
are working with a family $\mathcal{P}$ of densities over $\mathbb{R}$
that covers all finite means, has finite variances, and is closed
under convex combinations. Similar problems were considered by \citet{romano2004non}
and \citet{Donoho1988-hg}.

Using the Gleswer--Hwang theorem, it is easy to verify every confidence
set has infinite diameter with positive probability. Define the partition
$\Pi$ by $p,q\in\pi$ if and only if $E_{p}(X)=E_{q}(X)$, and let
$\left\Vert [p]\right\Vert =|E_{p}(X)|$. Let
\[
p_{n}(x)=\left(1-\frac{1}{n}\right)q_{0}(x)+\frac{1}{n}q_{n^{2}}(x),
\]
where $p_{0}$ has mean $0$ and $q_{n^{2}}$ has mean $n^{2}$. Then
$\left\Vert [p_{n}]\right\Vert =n$, the conditions of Theorem \ref{thm:Gleser--Hwang}
are satisfied, and every confidence set with level $\alpha>0$ has
infinite diameter with positive probability.

@@

Using Lemma \ref{lem:generalized shifted exponential} it is not hard
to show that the basic publication bias model (\ref{eq:selection for significance model})
is a member of the Gleser--Hwang class.
\begin{thm}
\label{thm:simple publication bias} Assume $n$ independent samples
from the basic publication bias model (\ref{eq:selection for significance model}).
Then, for any $n$, any confidence set for $\theta_{0},\tau$, or
$(\theta_{0},\tau)$ with level $\alpha>0$ will have infinite diameter
with positive probability. 
\end{thm}

@@

Let $f^{1},f^{2},\ldots,f^{K}$ be a sequence of densities, $\pi=(\pi^{1},\pi^{2},\ldots,\pi^{K})$
a probability vector, and $p=\sum_{k\leq K}\pi^{k}f^{k}$ a mixture
distribution. We will assume that the size of $[p]$ equals the size
of any of its mixture components $[f^{k}]$ for some size $\left\Vert \cdot\right\Vert $,
i.e., $\left\Vert [p]\right\Vert =\left\Vert [f^{k}]\right\Vert $
for all $k$. Why we do this will be clear in the proof of Theorem
\ref{thm:general publication bias}, but think of it this way: If
all of $p$s mixture components have the same mean, the mean of $p$
equals the mean of any $f^{k}$. 
\begin{lem}
\label{prop:Mixture model corollary} Let $\mathcal{P}$ be a class
of $K$-ary mixture distributions and $||[p]||$ be the assumption
above. Assume there is a sequence $p_{n}=\sum_{k\leq K}\pi_{n}^{k}f_{n}^{k}$
and a subset $K'$ such that 
\begin{enumerate}
\item For all $k\in K'$, there is a density $f^{k\star}$ such that $f_{n}^{k}$
converges to $f^{k\star}$ pointwise.
\item For all mixtures $p$, $\supp p\supseteq\supp f^{k\star}$ for some
$k\in K'$.
\item For all $k\in K'$, the size of $[f_{n}^{k}]$ goes to infinity, $\left\Vert [f_{n}^{k}]\right\Vert \to\infty$.
\item The density concentrates on the components indexed by $K'$, $\lim_{n\to\infty}\sum_{k\in K'}\pi_{n}^{k}=1$.
\end{enumerate}
Then every confidence set with level $\alpha>0$ has infinite diameter
with positive probability.
\end{lem}

\begin{proof}
We employ Theorem \ref{thm:Gleser--Hwang}. By (i) and (iv), $p_{n}$
converges pointwise to the density $\sum_{k\in K'}\pi_{n}^{k\star}f_{n}^{k\star}=p^{\star}$
. That $\supp p\supseteq p^{\star}$ follows from (ii) and (iv). Finally,
from the assumption that$\left\Vert [p_{n}]\right\Vert =\left\Vert [f_{n}^{k}]\right\Vert $,
we get that $\left\Vert [p_{n}]\right\Vert \to\infty$ too. 
\end{proof}
\begin{thm}
\label{thm:general publication bias} Assume $n$ independent samples
from the publication bias model (\ref{eq:selection for significance model}),
where the selection probability $\rho$ is unknown and $\alpha$ is
known. Then any confidence set for $\theta_{0},\tau$, or $(\theta_{0},\tau)$
will have infinite diameter with positive probability.
\end{thm}

\begin{proof}
\label{proof:general publication bias} Let $n=1$ and consider confidence
sets for $\theta_{0}$. Let $\Pi$ be the partition of $\mathcal{P}$
where $p,q\in\pi$ if and only if they share the same $\theta_{0}$,
and let $||[p]||=|\theta_{0}|$. Then $||f^{k}||=|\theta_{0}|$ from
the mixture representation (\ref{eq:mixture model formulation}).
Using Lemma \ref{lem:generalized shifted exponential}, we see that
$f^{k},k>1$ converges pointwise to a truncated exponential when $\theta_{0}=-n$
and $\sqrt{\tau^{2}+\sigma^{2}}=n^{1/2}$, so that (i), (ii), (iii)
of Proposition \ref{prop:Mixture model corollary} are satisfied with
$K'=K\backslash\{1\}$. The mixture probabilities for $k\neq K$ can
be fixed at e.g. $\pi=1/(K-1)$, and (iv) is satisfied as well. The
proofs for $||[p]||=\tau$ and $||[p]||=\sqrt{\tau^{2}+\theta_{0}^{2}}$
are similar and omitted. When $N>1$, expand the expression $\prod_{j=1}^{n}\sum_{k\leq K}\pi_{i}^{k}(\sigma_{j})f_{i}^{k}(\sigma_{j}),$and
use the same reasoning as in the first part of this proof.
\end{proof}

@@

The following sandwich convergence theorem is used in the proof of
the Gleser--Hwang theorem. 
\begin{lem}[{\citet[Exercise 16.4(a)]{billingsley1995probability}}]
\label{lem:Dominated covergence theorem} Suppose $a_{n},b_{n},f_{n}$
converge to $a,b,f$ and $a_{n}\leq f_{n}\leq b_{n}$ for all $n$.
If $\int a_{n}d\mu\to\int ad\mu$ and $\int b_{n}d\mu\to\int bd\mu$,
then $\int f_{n}d\mu\to\int fd\mu$ for any measure $\mu$.
\end{lem}

The proof of Theorem \ref{thm:Gleser--Hwang} closely follows the
proof of \citet[Theorem 1]{gleser1987nonexistence}.
\begin{proof}[Proof of Theorem \ref{thm:Gleser--Hwang}]
\label{proof:Gleser--Hwang}We can assume without loss of generality
that $\left\Vert [p_{n}]\right\Vert \geq n$, as we can choose a subsequence
if we have to. By definition of the diameter $D$ (\ref{eq:diameter})
we see that
\[
\{D\geq n\}=\{\omega\in\Omega\mid\textrm{there is a }\pi\textrm{ such that}\left\Vert \pi\right\Vert \geq n\textrm{ and }\omega\in R^{c}(\pi)\},
\]
and if $||[p_{n}]||\geq n$, then $R^{c}([p_{n}])\subseteq\{D\geq n\}$.
Since we assume that $\left\Vert [p_{n}]\right\Vert \geq n$ and 
\[
1-\alpha\leq P_{n}(R^{c}([p_{n}]))=\int_{R^{c}([p_{n}])}p_{n}d\mu
\]
by definition of a confidence set, we have that
\begin{equation}
0<1-\alpha\leq\int_{R^{c}([p_{n}])}p_{n}d\mu\leq\int_{D\geq n}p_{n}d\mu\label{eq:inequality with R^c}
\end{equation}
for all $n$. Since $p_{n}$ and $p^{\star}$ are densities,
\[
\lim_{n\to\infty}\int p_{n}d\mu=1=\int p^{\star}d\mu=\int\lim_{n\to\infty}p_{n}d\mu.
\]
This allows us to use Lemma \ref{lem:Dominated covergence theorem}
with $a_{n}=0$, $b_{n}=p_{n}$, and $f_{n}=1_{D\geq n}p_{n}$ and
conclude that
